\documentclass[sigconf,edbt]{acmart-edbt2019}

\usepackage{booktabs} % For formal tables
\usepackage{subfigure}
\usepackage{color}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}

\usepackage{caption}
\usepackage{color}
\usepackage[ruled]{algorithm}
\usepackage{algorithmic}

\newcommand{\ie}[0]{\textit{i.e.}}
\newcommand{\eg}[0]{\textit{e.g.}}
\newcommand{\etal}[0]{\textit{et al.}}
\newcommand{\wrt}[0]{\textit{w.r.t.}}


\newcommand{\keobf}{\textit{$(k,\epsilon)$-obf}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\genobf}{\texttt{\textbf{genObf}}}
\newcommand{\ere}{$\mathcal{E}RR-$eval}
\newcommand{\pg}{\mathcal{G}}
\newcommand{\Constraint}{$\mathcal{C}$}
\newcommand{\Number}{\|v\|}

\theoremstyle{plain}
\newtheorem{problem}{Problem}
\newtheorem{observation}{Observation}

\newcommand{\methodName}{Squid}
\newcommand{\capMethodName}{SQUID}
\newcommand{\soaName}{Obf}


% Copyright
\setcopyright{rightsretained}

% DOI
\acmDOI{}

% ISBN
\acmISBN{XXX-X-XXXXX-XXX-X}

%Conference
\acmConference[EDBT 2019]{22nd International Conference on Extending Database Technology (EDBT)}{March 26-29, 2019}{Lisbon, Portugal} 
\acmYear{2019}

\settopmatter{printacmref=false, printccs=false, printfolios=false}

\pagestyle{empty} % removes running headers


\begin{document}
\title{SIG Proceedings Paper in LaTeX Format}
\titlenote{Produces the permission block, and copyright information}
\subtitle{Extended Abstract}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}
  

\author{Ben Trovato}
\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \postcode{43017-6221}
}
\email{trovato@corporation.com}

\author{G.K.M. Tobin}
\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \postcode{43017-6221}
}
\email{webmaster@marysville-ohio.com}

\author{Lars Th{\o}rv{\"a}ld}
\authornote{This author is the
  one who did all the really hard work.}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla} 
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}
\author{Aparna Patel} 
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh} 
 \state{Arunachal Pradesh}
 \country{India}}
\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu} 
  \state{Beijing Shi}
  \country{China}
}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas} 
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P.~Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

% The default list of authors is too long for headers}
% \renewcommand{\shortauthors}{B. Trovato et al.}
\renewcommand{\shortauthors}{}


\begin{abstract}
Graphs in many real-world applications, such as social networks and business to business networks, are not deterministic but uncertain. Research in areas such as social science and viral marketing requires open access to these uncertain graphs, but publishing these datasets often risks exposing sensitive and private data. Current works mainly concentrate on privacy issues with deterministic graphs. The uncertain scenario is overlooked. 

In this paper, we study the problem of publishing uncertain graphs under the syntactic anonymity guarantee. We first demonstrate the limitations of conventional methods in the uncertain scenario. By disregarding the possible world semantics of uncertain graphs, they significantly disrupt the stochastic structure. We develop a syntactically private algorithm, Squid. Squid integrates the possible world semantics into the core of the anonymization. It enables a fine-grained, uncertainty-aware control over the injected noise in a novel way. We apply our method to real uncertain graphs and show its efficiency and practical utility.
\end{abstract}

%
% % The code below should be generated by the tool at
% % http://dl.acm.org/ccs.cfm
% % Please copy and paste the code instead of the example below. 
% %
% \begin{CCSXML}
% <ccs2012>
%  <concept>
%   <concept_id>10010520.10010553.10010562</concept_id>
%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%   <concept_significance>500</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010575.10010755</concept_id>
%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%   <concept_significance>300</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010553.10010554</concept_id>
%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10003033.10003083.10003095</concept_id>
%   <concept_desc>Networks~Network reliability</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
% </ccs2012>  
% \end{CCSXML}
% 
% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}


% \keywords{ACM proceedings, \LaTeX, text tagging}


\maketitle

\input{intro.tex}
\input{relates.tex}
\input{notation.tex}
\input{state_of_art.tex}
\input{squid.tex}
\input{squid_ex/exp.tex}
\input{conclusion.tex}

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs} 

\end{document}
